A comprehensive framework to capture the arcana of neuroimaging analysis

### 2019-03-14 manuscript/manuscript.tex
ensured that mappings have the right key/value pairings

The syntax for pipeline construction is inspired by a proposed form for Nipype v2.0
(\url{github.com/nipy/nipype/issues/2539}).
Within a pipeline constructor method, a Pipeline object is constructed by the \emph{Study.pipeline} method
(Figure \ref{fig:pipeline_constructor}). At initialisation, each pipeline is given a name,
which must be unique amongst the pipelines constructed by the Study. The methods implemented
by the pipeline can be characterised by providing a the list of scientific references
and a text description to the \emph{references} and \emph{desc} keyword arguments, respectively.

@@

Pipeline constructor methods can be overridden in subclasses like any Python
method. Often the overriding method will call the superclass method
to construct a pipeline, apply modifications and return the
modified pipeline. In this scenario, references to the data
specification in the superclass method can be mapped onto different
entries in the table of the subclass by providing the \emph{input\_map} and
\emph{output\_map} keyword arguments when calling the superclass method.
Additionally the name of the pipeline can be altered by providing the \emph{name}
argument, which is useful when creating multiple  constructor methods from the
one base method. In these scenarios it is important to
also pass the the wildcard keyword arguments of the overriding method to the
\emph{name\_maps} keyword argument of the superclass method, to allow the
overriding method to be overridden in turn.

@@

Sub-studies are aggregated in the \emph{sub-study} \emph{specification
table} of a MultiStudy class via a list of \emph{SubStudySpec} objects
in the \emph{add\_sub\_study\_specs} class attribute in the manner of
data and parameter specifications. A SubStudySpec consists of a name, a
Study class, and a \emph{name map} dictionary\emph{.} The name map
dictionary maps data and parameter specification names from the
sub-study namespace to the namespace of the MultiStudy class.

Entries in the specification tables of sub-study classes that are not
referenced in the sub study's name map are implicitly mapped to the
MultiStudy namespace by the MultiStudyMetaClass during construction of the MultiStudy class,
using the name of the sub-study as a prefix.
If the specification is derived, then its associated pipeline constructor method
is also mapped into the MultiStudy namespace. For example, \emph{derived1} in
\emph{sub\_study2} would be mapped to \emph{sub\_study2\_derived1} along
with the method \emph{sub\_study2\_pipeline1}.

@@

\emph{ModulesEnvironment} objects can be used if environment
modules \citep{furlani_modules:_1991} are installed on the system (typical in many
HPC systems). In this case, environment modules are loaded before a workflow node is run,
based on the requirements specified for the node during construction of the pipeline
(see \emph{Pipeline constructors}), and then unloaded afterwards. Mappings from non-standard
module names installed on the system to those expected by the Study can be
can be passed as a dictionary to the \emph{packages\_map} keyword argument
at initialisation. Likewise non-standard versions for packages can be mapped onto
requirements using the \emph{versions\_map} keyword argument.

>>>>

The syntax for pipeline construction is inspired by a proposed form for Nipype v2.0
(\url{github.com/nipy/nipype/issues/2539}).
Within a pipeline constructor method, a Pipeline object is constructed by the \emph{Study.pipeline} method
(Figure \ref{fig:pipeline_constructor}). At initialisation, each pipeline is given a name,
which must be unique amongst the pipelines constructed by the Study. The methods implemented
by the pipeline can be characterised by providing a the list of citations
and a text description to the \emph{citations} and \emph{desc} keyword arguments, respectively.

@@

Pipeline constructor methods can be overridden in subclasses like any Python
method. Often the overriding method will call the superclass method
to construct a pipeline, apply modifications and return the
modified pipeline. In this scenario, references to the data
specification in the superclass method can be mapped onto different
entries in the table of the subclass by providing the \emph{input\_map} and
\emph{output\_map} keyword arguments when calling the superclass method.
Additionally the name of the pipeline can be altered by providing the \emph{name}
argument, which is useful when creating multiple pipeline constructor methods
from a single base method. In these scenarios it is important to
also pass the the wildcard keyword arguments of the overriding method to the
\emph{name\_maps} keyword argument of the superclass method to allow the
overriding method to be overridden in turn.

@@

Sub-studies are aggregated in the \emph{sub-study} \emph{specification
table} of a MultiStudy class via a list of \emph{SubStudySpec} objects
in the \emph{add\_sub\_study\_specs} class attribute in the manner of
data and parameter specifications. A SubStudySpec consists of a name, a
Study class, and a \emph{name map} dictionary\emph{.} The name map
dictionary maps data and parameter specification names from the
sub-study namespace to the namespace of the MultiStudy class, i.e.
the dictionary keys are in the sub-study namespace and the dictionary
values are in the global namespace.

Entries in the specification tables of sub-study classes that are not
referenced in the sub study's name map are implicitly mapped to the
MultiStudy namespace by the MultiStudyMetaClass during construction of the
MultiStudy class using the name of the sub-study as a prefix.
If the implicitly mapped specification is derived, then its associated pipeline
constructor method is also mapped into the MultiStudy namespace with a prefix.
For example, \emph{derived1} in \emph{sub\_study2} would be mapped to
\emph{sub\_study2\_derived1} along with the method
\emph{sub\_study2\_pipeline1}.

@@

\emph{ModulesEnvironment} objects can be used if environment
modules \citep{furlani_modules:_1991} are installed on the system (typical in many
HPC systems). In this case, environment modules are loaded before a workflow node is run,
based on the requirements specified for the node during construction of the pipeline
(see \emph{Pipeline constructors}), and then unloaded afterwards. Mappings from non-standard
module names installed on the system to those expected by the Study can be
can be passed as a dictionary to the \emph{packages\_map} keyword argument
at initialisation. Likewise non-standard versions for packages can be mapped
onto the versioning system of a requirement using the \emph{versions\_map}
keyword argument.
